%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Hazim Mohamed} % Your name
\address{288 Bloomfield St, Athens, Georgia 30605} 
\address{(+1)4702651854 \\ hazim.mohamed@uga.edu} 

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Georgia} \hfill {\em August 2017 - Present}
\\ Franklin College of Arts and Sciences
\\ Bachelors in Computer Science

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{Google, Chrome Storage}{May 2020 - Present}{Software Engineer Intern}{}
\item Used C++ and JavaScript to add drag and drop support for an experimental web feature allowing websites
    to access users' native file systems.
\item Gained experience writing concurrent code and drafting W3 web specs.
\end{rSubsection}

\begin{rSubsection}{Google, Search Ads 360}{May 2019 - August 2019}{Software Engineer Intern}{}
\item Used C++ to create a tool to automate
      a task that previously took six days of an engineer's careful attention. It is currently in production and used daily.
\item Updated the internal lock server infrastructure to support storing comment information 
      to protect against user errors.
\end{rSubsection}


\begin{rSubsection}{University of Georgia, Franklin College of Arts and Sciences}{January 2019 - May 2019}{Computer Science Teaching Assistant}{}
\item Helped teach a course that taught first to second-year students Object Oriented Programming concepts in Java, basic Java GUI, and advanced Git version control

\item Hosted office hours three times a week to answer student questions and debug student code

\end{rSubsection}

\begin{rSubsection}{Cisco Systems}{May 2016 - July 2016}{Student Intern}{}
\item Designed an app that won second place in the Cisco App Development competition.

\item Learned about the inner workings of the most common Cisco products mostly centering around Voice over IP and network architecture
    
\end{rSubsection}

\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Personal Projects}
{\bf Rapbot}\\
{ Created an algorithm that uses various API calls and graph algorithms to generate wrap songs from Wikipedia articles. }

{\bf Litness}\\
{ Created an app using Android Studio that uses user location data to help college students track local bar occupancy. The app would then use that data to help bars improve marketing and anticipate spikes in occupancy. This app won the UGA 2019 Hackathon in multiple categories.}

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

{\bf Programming Languages:} Java (very familiar), C++ (very familiar), Python (very familiar), JavaScript (very familiar), LabVIEW (familiar),  C\# (familiar), SQL (familiar) \\
{\bf Software \& Frameworks:} \ Android Studio, Git, Unity, Angular \\

\end{rSection}

%----------------------------------------------------------------------------------------
%	AWARDS AND ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------


\begin{rSection}{Awards and Achievements}

2019 UGA Hacks Winner in Multiple Categories \\
1st Place in Georgia in First Robotics Competition; 6th in the world \\

\end{rSection}

\end{document}